Different rules for binocular combination of luminance in cortical and subcortical pathways

### 2022-09-25 manuscript.Rmd
Update manuscript.Rmd

knitr::include_graphics('local/Figures/pupildata.pdf')

@@

knitr::include_graphics('local/Figures/EEGdata.pdf')

@@

knitr::include_graphics('local/Figures/TFdata.pdf')

@@

@@

knitr::include_graphics('local/Figures/matchingdata.pdf')

@@

# settings for sampler 
numSavedSteps <- 20000    # total number of MCMC steps
adaptSteps = 1000  # Number of steps to "tune" the samplers
burnInSteps = 2000 
thinSteps <- 10
nChains = 8
ncores <- detectCores()/2  # because of multi-threading, this is usually double the true number of physical cores, so we halve the number as Stan can only use physical cores
options(mc.cores=ncores)

@@

plotlims <- c(-48,12,0,0.3) 
ticklocsx <- seq(-48,12,12)    
ticklocsy <- seq(0,0.3,0.1)    
ticklabelsx <- c('1/256','1/64','1/16','1/4','1','4')        
ticklabelsy <- ticklocsy    # set labels for y ticks

@@

legend(-48,0.3,c('Prior','Pupillometry','EEG 1F','EEG 2F','Matching'),col=c('black',colpal[3:6]),lwd=c(1,3,3,3,3),lty=1, box.lwd=2, bg='white')

text(9,0.28,'(e)',cex=1.25,adj=0.5)

@@

par(pty="s")  # make axis square
plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   # create an empty axis of the correct dimensions
axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)    
axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
mtext(text = ticklabelsx, side = 1, at=ticklocsx)    
mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)  
title(xlab="Target contrast (dB)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    # titles for axes
title(ylab="Amplitude at 2Hz (mm)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)

@@

text(17,0.038,'(a)',adj=0.5,cex=2.5)

@@

legend(21,0.8,c('Monocular','Binocular','Dichoptic','Dichoptic cross'),lwd=3,col=colpal[condlist],box.lwd=2)

text(17,0.75,'(b)',adj=0.5,cex=2.5)

@@

legend(21,0.8,c('Monocular','Binocular','Dichoptic','Dichoptic cross'),lwd=3,col=colpal[condlist],box.lwd=2)

text(17,0.75,'(c)',adj=0.5,cex=2.5)

@@

@@

@@

  pdf(paste0(figdir,"modelfigure.pdf"), bg="transparent", height = 10, width = 20)
  par(mar=c(0.1,0.1,0.1,0.1))
  plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(0,1), ylim=c(0,1))

  grid.picture(p1,x=0.125,y=0.75,width=0.25,height=1)
  grid.picture(p2,x=0.375,y=0.75,width=0.25,height=1)
  grid.picture(p3,x=0.125,y=0.25,width=0.25,height=1)
  grid.picture(p4,x=0.375,y=0.25,width=0.25,height=1)

  grid.picture(p5,x=0.75,y=0.5,width=0.5,height=1)

@@

  file.remove(c('CRF1e.ps','CRF2e.ps','CRF1p.ps','matchingmodel.ps','posteriors.ps'))
  file.remove(c('CRF1e.ps.xml','CRF2e.ps.xml','CRF1p.ps.xml','matchingmodel.ps.xml','posteriors.ps.xml'))

@@

knitr::include_graphics('local/Figures/modelfigure.pdf')

>>>>

knitr::include_graphics(paste0(figdir,'pupildata.pdf'))

@@

knitr::include_graphics(paste0(figdir,'EEGdata.pdf'))

@@

knitr::include_graphics(paste0(figdir,'TFdata.pdf'))

@@

save(file=paste0(datadir,'meanmatching.RData'),list=c('meanthresh','SEthresh','allthresh'))

load(paste0(datadir,'meanmatching.RData'))

@@

knitr::include_graphics(paste0(figdir,'matchingdata.pdf'))

@@

# settings for sampler 
numSavedSteps <- 100000    # total number of MCMC steps
adaptSteps <- 1000  # Number of steps to "tune" the samplers
burnInSteps <- 2000 
thinSteps <- 10
nChains <- 8
ncores <- detectCores()/2  # because of multi-threading, this is usually double the true number of physical cores, so we halve the number as Stan can only use physical cores
options(mc.cores=ncores)

@@

plotlims <- c(-48,12,0,0.5) 
ticklocsx <- seq(-48,12,12)    
ticklocsy <- seq(0,0.5,0.1)    
ticklabelsx <- c('1/256','1/64','1/16','1/4','1','4')        
ticklabelsy <- ticklocsy    # set labels for y ticks

@@

legend(-48,0.5,c('Prior','Pupillometry','EEG 1F','EEG 2F','Matching'),col=c('black',colpal[3:6]),lwd=c(1,3,3,3,3),lty=1, box.lwd=2, bg='white')

text(9,0.48,'(i)',cex=1.25,adj=0.5)

@@

par(pty="s")  # make axis square
plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])
axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)    
axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
mtext(text = ticklabelsx, side = 1, at=ticklocsx)    
mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)  
title(xlab="Target contrast (dB)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    
title(ylab="Amplitude at 2Hz (mm)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)

@@

text(17,0.038,'(e)',adj=0.5,cex=2.5)

@@

# legend(21,0.8,c('Monocular','Binocular','Dichoptic','Dichoptic cross'),lwd=3,col=colpal[condlist],box.lwd=2)

text(17,0.75,'(f)',adj=0.5,cex=2.5)

@@

# legend(21,0.8,c('Monocular','Binocular','Dichoptic','Dichoptic cross'),lwd=3,col=colpal[condlist],box.lwd=2)

text(17,0.75,'(g)',adj=0.5,cex=2.5)

@@

text(10,117.5,'(h)',adj=0.5,cex=2.5)

postscript("pdata.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 5.5)

for (cond in 1:3){
  lines(contrastsdB,abs(cleanmeansP[cond,]), col=colpal[cond], lwd=3, cex=0.5)
  points(contrastsdB,abs(cleanmeansP[cond,]), pch = 20+cond, col='black', bg=colpal[cond], cex=1.6, lwd=3)   # draw the data points themselves
}  
cond <- 6
  lines(contrastsdB,abs(cleanmeansP[cond,]), col=colpal[cond], lwd=3, cex=0.5)
  points(contrastsdB,abs(cleanmeansP[cond,]), pch = 25, col='black', bg=colpal[cond], cex=1.6, lwd=3)   # draw the data points themselves

legend(21,0.03,c('Monocular','Binocular','Dichoptic','Dichoptic cross'),pch=c(21:23,25),pt.bg=colpal[c(1:3,6)],pt.lwd=3,pt.cex=1.6,box.lwd=2)
text(17,0.028,'(a)',adj=0.5,cex=2.5)

postscript("edata.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 5.5)

par(pty="s")  # make axis square
plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])
axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
mtext(text = ticklabelsx, side = 1, at=ticklocsx)     # add the tick labels
mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1) 
title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)  
title(ylab="Amplitude (µV) at 2Hz", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)

for (cond in 1:3){
  lines(contrastsdB,abs(cleanmeansEav[cond,]), col=colpal[cond], lwd=3, cex=0.5)
  points(contrastsdB,abs(cleanmeansEav[cond,]), pch = 20+cond, col='black', bg=colpal[cond], cex=1.6, lwd=3)   # draw the data points themselves
}  
cond <- 6
  lines(contrastsdB,abs(cleanmeansEav[cond,]), col=colpal[cond], lwd=3, cex=0.5)
  points(contrastsdB,abs(cleanmeansEav[cond,]), pch = 25, col='black', bg=colpal[cond], cex=1.6, lwd=3)   # draw the data points themselves

# legend(22,0.8,c('Monocular','Binocular','Dichoptic','Dichoptic cross'),pch=c(21:23,25),pt.bg=colpal[c(1:3,6)],pt.lwd=3,pt.cex=1.6,box.lwd=2)
text(17,0.75,'(b)',adj=0.5,cex=2.5)

postscript("edata2.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 5.5)

par(pty="s")  # make axis square
plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])
axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
mtext(text = ticklabelsx, side = 1, at=ticklocsx)     # add the tick labels
mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1) 
title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)  
title(ylab="Amplitude (µV) at 4Hz", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)

for (cond in 1:3){
  lines(contrastsdB,abs(cleanmeansE2av[cond,]), col=colpal[cond], lwd=3, cex=0.5)
  points(contrastsdB,abs(cleanmeansE2av[cond,]), pch = 20+cond, col='black', bg=colpal[cond], cex=1.6, lwd=3)   # draw the data points themselves
}  
cond <- 6
  lines(contrastsdB,abs(cleanmeansE2av[cond,]), col=colpal[cond], lwd=3, cex=0.5)
  points(contrastsdB,abs(cleanmeansE2av[cond,]), pch = 25, col='black', bg=colpal[cond], cex=1.6, lwd=3)   # draw the data points themselves

# legend(22,0.8,c('Monocular','Binocular','Dichoptic','Dichoptic cross'),pch=c(21:23,25),pt.bg=colpal[c(1:3,6)],pt.lwd=3,pt.cex=1.6,box.lwd=2)
text(17,0.75,'(c)',adj=0.5,cex=2.5)

         if (!file.exists(paste0(datadir,'meanmatching.RData'))){
           # download it from OSF
           if (!exists('osffilesP')){
           osfnode <- '2qu6y'
           osfproject <- osf_retrieve_node(osfnode)
          osffilesP <- osf_ls_files(osfproject,n_max=300)}
          fid <- which(osffilesP$name=='meanmatching.RData')
          osf_download(osffilesP[fid,],datadir,progress=TRUE)
         }

load(paste0(datadir,'meanmatching.RData'))

postscript("matchingdata.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 5.5)

plotlims <- c(0,125,0,125)  
ticklocs <- seq(0,125,25)   
ratiosL <- c(1, 1, 1, 1, 1, 0.75, 0.5, 0.25, 0)
ratiosR <- c(0, 0.25, 0.5, 0.75, 1, 1, 1, 1, 1)

  # if ((SEthresh[matchlev,cond]+meanthresh[matchlev,cond])<42){
  # arrows(ratiosR[cond]*10^(meanthresh[matchlev,cond]/20),ratiosL[cond]*10^(meanthresh[matchlev,cond]/20),ratiosR[cond]*10^((SEthresh[matchlev,cond]+meanthresh[matchlev,cond])/20),ratiosL[cond]*10^((SEthresh[matchlev,cond]+meanthresh[matchlev,cond])/20),length=0.015, angle=90, lwd=2)
  # }
  # 
  # # plot as an arrow if exceeding the axis limits
  # if ((SEthresh[matchlev,cond]+meanthresh[matchlev,cond])>42){
  # arrows(ratiosR[cond]*10^(meanthresh[matchlev,cond]/20),ratiosL[cond]*10^(meanthresh[matchlev,cond]/20),125,ratiosL[cond]*10^((SEthresh[matchlev,cond]+meanthresh[matchlev,cond])/20),length=0.035, angle=45, lwd=2)
  # }

  # arrows(ratiosR[cond]*10^(meanthresh[matchlev,cond]/20),ratiosL[cond]*10^(meanthresh[matchlev,cond]/20),ratiosR[cond]*10^((meanthresh[matchlev,cond]-SEthresh[matchlev,cond])/20),ratiosL[cond]*10^((meanthresh[matchlev,cond]-SEthresh[matchlev,cond])/20),length=0.015, angle=90, lwd=2)
}
}

@@

  PostScriptTrace('pdata.ps')
  p6 <- readPicture('pdata.ps.xml')
  PostScriptTrace('edata.ps')
  p7 <- readPicture('edata.ps.xml')
  PostScriptTrace('edata2.ps')
  p8 <- readPicture('edata2.ps.xml')
  PostScriptTrace('matchingdata.ps')
  p9 <- readPicture('matchingdata.ps.xml')

@@

  pdf(paste0(figdir,"modelfigure.pdf"), bg="transparent", height = 10, width = 30)
  par(mar=c(0.1,0.1,0.1,0.1))
  plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(0,1), ylim=c(0,1))

  grid.picture(p1,x=1/12,y=0.25,width=1/6,height=1)
  grid.picture(p2,x=3/12,y=0.25,width=1/6,height=1)
  grid.picture(p3,x=5/12,y=0.25,width=1/6,height=1)
  grid.picture(p4,x=7/12,y=0.25,width=1/6,height=1)

  grid.picture(p5,x=5/6,y=0.5,width=1/3,height=1)

  grid.picture(p6,x=1/12,y=0.75,width=1/6,height=1)
  grid.picture(p7,x=3/12,y=0.75,width=1/6,height=1)
  grid.picture(p8,x=5/12,y=0.75,width=1/6,height=1)
  grid.picture(p9,x=7/12,y=0.75,width=1/6,height=1)

@@

  file.remove(c('CRF1e.ps','CRF2e.ps','CRF1p.ps','matchingmodel.ps','matchingdata.ps','pdata.ps','edata.ps','edata2.ps','posteriors.ps'))
  file.remove(c('CRF1e.ps.xml','CRF2e.ps.xml','CRF1p.ps.xml','matchingmodel.ps.xml','matchingdata.ps.xml','pdata.ps.xml','edata.ps.xml','edata2.ps.xml','posteriors.ps.xml'))

@@

knitr::include_graphics(paste0(figdir,'modelfigure.pdf'))
